Computing Entropies With Nested Sampling

### 2017-08-11 paper/response.tex

Sorry about the confusion. I was trying to represent the operation of
appending one new element (a depth estimate)
to an existing list, which in Python is {\tt +}
and in Haskell is {\tt ++}. The square brackets were meant to represent
the wrapping of a value within a list (to make a list of length one),
since an append function is probably a function of two lists.
All of this was too obscure. I have replaced it with
\begin{align}
$\widehat{\mathbf{h}} \leftarrow \textnormal{append}\big(\widehat{\mathbf{h}}, k/N\big)$
\end{align}
which is hopefully more understandable.

{\quote
3. In Section 2, the author writes "1. Points can be generated from the prior..."  Please clarify what is meant by "points".  Does the author mean samples?}

Yes. I have changed points to samples.

{\quote
The author writes:
"The former measures the degree to which one question answers another ex ante, and is a function of two questions. The latter measures the degree to which a statement answered a question ex post, and is a function of a question and a statement."
which reveals that the author has really have been thinking about questions!}

I'm glad you liked it! If you found this interesting, check out the foundations
work of Kevin Knuth, which I find fascinating.

{\quote
The author also writes:
"The mutual information is another way of describing the relevance of the data to the parameters. its definition, and relation to other quantities"
As far as I am aware, this is a novel way of thinking about mutual information!  Very nice!
In addition, I did not know that it could be written as the expected value of KL over datasets, which is fascinating.}

Thanks! In most information theory textbooks, these things are written in
terms of abstract `random variables' $X$ and $Y$. One of my subsidiary
goals in this paper was to discuss this stuff in terms and notation more
familiar to Bayesians.

### 2017-08-11 paper/ms.tex
More work on the revision

It is important to distinguish between $H(\x | \d)$ and the
entropy of $\x$ given a particular value of $\d$, which might be written
$H(\x | \d=\d_0)$.
The former measures the degree to which one question answers
another {\em ex ante}, and is a function of two questions.
The latter measures the degree to which a {\em statement} answered a question
{\em ex post}, and is a function of a question and a statement.

@@

Nested Sampling (NS), introduced by
\citet{skilling2006nested}, is an algorithm whose aim is
to calculate the evidence
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. The original NS algorithm, and variations
within the same family \citep{feroz2009multinest, dns, handley2015polychord},
have become popular tools in Bayesian data analysis
\citep{knuth2015bayesian, pullen2014bayesian, exoplanet} and have also
found use in statistical physics \citep{partay2010efficient,
baldock2016determining, martiniani2014superposition}, which was another of
its aims.

>>>>

It is important to distinguish between $H(\x | \d)$ and the
entropy of $\x$ given a particular value of $\d$, which might be written
$H(\x | \d=\d_{\rm observed})$.
The former measures the degree to which one question answers
another {\em ex ante}, and is a function of two questions.
The latter measures the degree to which {\revision a question remains unresolved
after conditioning on a specific statement ({\em ex post})},
and is a function of a question and a statement.

@@

Nested Sampling (NS), introduced by
\citet{skilling2006nested}, is an algorithm whose aim is
to calculate the evidence
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. The original NS algorithm, and variations
within the same family \citep{feroz2009multinest, dns, handley2015polychord},
have become popular tools in Bayesian data analysis
\citep{knuth2015bayesian, pullen2014bayesian, exoplanet} and have also
found use in statistical physics \citep{partay2010efficient,
baldock2016determining, martiniani2014superposition}, which was another of
its aims.
{\revision
NS also estimates the Kullback-Leibler divergence from the prior
$\pi(\x)$ to the posterior $\pi(x)L(x)/Z$, which Skilling calls the
information. This is a measure of how much was learned about $\x$
from the specific dataset, and is also useful for defining a termination
criterion for NS.}
